---
title: "Readme"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
The purpose of this readme is to explain the code and structure in completing the assessment for the first part of the data science course. This readme outlines the data, packages and codes used and guides the reader as to how each question of the assessment was answered. Each question is answered in a separate project. 

To get started, the different projects was created for question 1, question 2 and question 3. The following code was used:
```{r eval=FALSE, include=FALSE}
library(Texevier)
Texevier::create_template(directory = "C:/Users/E7450/Documents/Maties_WERK/Meesters/Data science/Nico/Assessment", template_name = "Question1")
Texevier::create_template(directory = "C:/Users/E7450/Documents/Maties_WERK/Meesters/Data science/Nico/Assessment", template_name = "Question2")
Texevier::create_template(directory = "C:/Users/E7450/Documents/Maties_WERK/Meesters/Data science/Nico/Assessment", template_name = "Question3")
```


# Question 1
This question addresses some claims a friend made regarding movie critics that perfectly predict films’ popularity and profitability amongst audiences. This was not the case during the mid 2000s. This question tests some of the friend's theories by addressing three of the statements she made.

The following packages were used:
```{r}
pacman::p_load(tidyverse, ggthemes)
```


## Loading in data
The data for each question has been unzipped and put under the data folder of each question folder. The data for the first question consists of a csv file. This file contains information on the name of various movies, the year during which the movie was released, each movie's production studio, its audience score and Rotten Tomatoes score, as well as the profitability of the movie.
The data was loaded as follows:
```{r}
MovieData <- read.csv("Question1/data/Movies.csv")
```


## The first statement 
The first point my friend made is: "I firmly remember that Rotten Tomatoes was always a great review platform - and if a movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above 85% every time."

To address this point, I drew a graph that indicates the ratings audiences gave movies that had a rating of more than 80% on Rotten Tomatoes. 
This was done by creating a function called RottenT_plot that draws the graph using only the movies that had a Rotten Tomatoes score above 80%. This function is stored in the code folder of the question 1 folder. This function was then sourced in and the relevant input was provided to produce the graph.

The movies were grouped into their relative genres to make it easier to see what the rating of audiences were. This graph indicates that animation movies that had a rating of more than 80% on Rotten Tomatoes, had audience scores above 85%. Therefore, for animation movies, my friend's statement is true. However, for all the other genres my friend's statement is not true since the audience scores were below 85%. Therefore, my friend's statement regarding movies having high audience scores if they have a high Rotten Tomatoes score is incorrect. 

```{r}
source("Question1/code/RottenT_plot.R")
graph_1 <- RottenT_plot(MovieData, xaxis_size = 5, xaxis_rows = 3)
graph_1
```

## The second statement






# Question 2



# Question 3
For this question, the answers have been presented in a Texevier pdf.



