---
title: "Profitable movies"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose
This document addresses some claims a friend made regarding movie critics that perfectly predict films’ popularity and profitability amongst audiences. This document show that this was not the case during the mid 2000s by addressing three of the statements she made.

The following packages were used:
```{r}
pacman::p_load(tidyverse)
```

The data is loaded as follows:
```{r}
MovieData <- read.csv("Question1/data/Movies.csv")
```


# The first statement
The first statement my friend made is: "I firmly remember that Rotten Tomatoes was always a great review platform - and if a movie had a rating of more than 80% on Rotten Tomatoes, audiences would rate it above 85% every time."

To address this point, Figure \ref{Figure1} was drawn that indicates the ratings audiences gave movies that had a rating of more than 80% on Rotten Tomatoes. 
The movies are grouped into their relative genres to make it easier to see what the rating of audiences were. Figure \ref{Figure1} indicates that animation movies that had a rating of more than 80% on Rotten Tomatoes, had audience scores above 85%. Therefore, for animation movies, my friend's first statement is true. However, for all the other genres my friend's statement is not true since the audience scores were below 85%. Therefore, my friend's statement regarding movies having high audience scores if they have a high Rotten Tomatoes score is incorrect. 
```{r, fig.align = 'center', fig.cap = "Audience scores(%)\\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 7}
source("code/RottenT_plot.R")
graph_1 <- RottenT_plot(MovieData, xaxis_size = 5, xaxis_rows = 3)
graph_1
```


# The second statement
The second statement my friend made is: "Disney films may not have the highest grossing numbers, but they’ve always been the most profitable of all the leading studios."

To test this statement, Figure \ref{Figure2} is presented below. This graph compares the profitability of all the leading studios. Figure \ref{Figure2} indicates that Independent was the most profitable studio between 2007 and 2011, as it had the highest profitability (just under 120%). Disney's profitability was around 40% which is much lower than that of Independent. Therefore, my friend's second statement regarding Disney being the most profitable studio of all the leading studios is incorrect. 
```{r, fig.align = 'center', fig.cap = "Studio's Profitability(%)\\label{Figure2}", fig.ext = 'png', fig.height = 5, fig.width = 7}
source("code/Profitability_plot.R")
graph_2 <- Profitability_plot(MovieData, xaxis_size = 10, xaxis_rows = 10)
graph_2
```


# The third statement


